### 2024-09-20 cognitive-bias.qmd
20240920 - prospect theory

@@

Dunning–Krueger Effect: Confidence as a Function of Competence. Adapted from <https://commons.wikimedia.org/wiki/File:Effet_Dunning-Kruger.svg>.
:::

@@

Dunning–Krueger Effect: Perceived Performance as a Function of Actual Performance. Adapted from <https://commons.wikimedia.org/wiki/File:Dunning-kruger_effect_-_percentile.svg>.
:::

>>>>

Principles of prospect theory and loss aversion bias are depicted in @fig-prospectTheory.

::: {#fig-prospectTheory}
![](images/prospectTheory.png)

Prospect Theory and Loss Aversion: People Tend to Weigh Losses More Heavily Than Gains. Adapted from <https://commons.wikimedia.org/wiki/File:Graphique_th%C3%A9orie_des_perspectives.svg>.
:::

@@

Dunning–Krueger Effect: Confidence as a Function of Competence. People with low competency in a task tend to overestimate their ability. Adapted from <https://commons.wikimedia.org/wiki/File:Effet_Dunning-Kruger.svg>.
:::

@@

Dunning–Krueger Effect: Perceived Performance as a Function of Actual Performance. People who perform poorly in a task tend to overestimate their performance. Adapted from <https://commons.wikimedia.org/wiki/File:Dunning-kruger_effect_-_percentile.svg>.
:::
